01_pca

### 2019-04-24 analysis/01_pca_all.Rmd
more work on spanish translations

# pca
pca <- prcomp(t(counts))
autoplot(pca, data = samples, colour = 'tissue') 
autoplot(pca, data = samples, colour = 'sex') 
autoplot(pca, data = samples, colour = 'treatment') 
autoplot(pca, data = samples, colour = 'tissue', shape = "sex") 
autoplot(pca, data = samples, colour = 'tissue', shape = "sex", alpha = "treatment")
autoplot(pca, data = samples, colour = 'treatment', shape = "sex", alpha = "tissue")

@@

# probability ellipse
autoplot(pam(t(counts), 3), frame = TRUE, frame.type = 'norm')
```

@@

en <- p + labs(subtitle = "PCA plot in English") +
  scale_colour_discrete(name = "colour", labels = c("rosado", "verde", "azul")) +
  scale_shape_discrete(name = "shape", labels = c("circle", "square")) +
  theme_rmh()

>>>>

# pca
pca <- prcomp(t(counts))

autoplot(pca, data = samples, colour = 'tissue') 
autoplot(pca, data = samples, colour = 'sex') 
autoplot(pca, data = samples, colour = 'treatment') 
autoplot(pca, data = samples, colour = 'tissue', shape = "sex") 
autoplot(pca, data = samples, colour = 'tissue', shape = "sex", alpha = "treatment")
autoplot(pca, data = samples, colour = 'treatment', shape = "sex", alpha = "tissue")

@@

# probability ellipse
autoplot(pam(t(counts), 3), frame = TRUE, frame.type = 'norm')

head(pca)
```

@@

en <- p + labs(subtitle = "PCA plot in English") +
  scale_colour_discrete(name = "colour", labels = c("pink", "green", "blue")) +
  scale_shape_discrete(name = "shape", labels = c("circle", "square")) +
  theme_rmh()
